A concise manual to\\\textsc{DEVS Ex Machina}

### 2015-05-26 manual/tex/controller.tex
Updated manual (Controller), added example simulations

	\begin{tabular}{l|l}
	\textsf{Option} & \textsf{Meaning} \\
	\texttt{OPTIMISTIC} & \emph{Optimistic PDEVS Simulation} \\
	\texttt{CONSERVATIVE} & \emph{Conservative PDEVS Simulation} \\
	\end{tabular} \newline

	The default is \emph{OPTIMISTIC} \newline
	\textit{[This option is disregarded if you do not run PDEVS]}
\\\\
\textit{coreAmount} & The amount of cores the simulation will run on \newline
						\textit{[This option is disregarded if you do not run PDEVS]} \newline
						By default this is 1
\\\\
\textit{saveInterval} & This value decides how often the simulation is saved and the tracing output dumped. A value of 3 would mean that this happens every 3 simulation cycles. \newline
						The default value is 5
\\\\
\textit{allocator} & By default this is the included \textsl{SimpleAllocator}
\\\\
\end{tabular}\\
\\
After you are done setting the right options, you can generate a \textbf{controller} by using \textsl{ControllerConfig}'s \textsl{createController} method. All further interactions with your simulation are done through this controller.\\
\\
As a short example, this configuration would give you a Classic DEVS named \texttt{foosim} that saves every 8 cycles:
\begin{verbatim}
ControllerConfig conf = ControllerConfig();
conf.name = "foosim";
conf.saveInterval = 8;

@@

\subsubsection{Loading a previous simulation}
Loading a previous simulation from a savefile follows the same procedure as setting up a regular simulation for the most part. First the simulation is configured (optionally by using the ControllerConfig object as described above), then instead of loading a new model, you can use the Controller's \textsl{load} method to load the data of your previous simulation.\\
\emph{Important: To load a simulation \textbf{do not} have to use the same configuration!}

>>>>

	\begin{tabular}{l|l}
	\textsf{Option} & \textsf{Meaning} \\
	\texttt{OPTIMISTIC} & \emph{Optimistic PDEVS Simulation} \\
	\texttt{CONSERVATIVE} & \emph{Conservative PDEVS Simulation} \\
	\end{tabular} \newline
	\textit{[This option is disregarded if you do not run PDEVS]} \newline
	The default is \emph{OPTIMISTIC}

\\\\
\textit{coreAmount} & The amount of cores the simulation will run on \newline
						\textit{[This option is disregarded if you do not run PDEVS]} \newline
						By default this is 1
\\\\
\textit{saveInterval} & This value decides how often the simulation is saved and the tracing output dumped. A value of 3 would mean that this happens every 3 simulation cycles. \newline
\textit{[This option is disregarded if you do not run CLASSIC or DSDEVS]} \newline
						The default value is 5
\\\\
\textit{allocator} & By default this is the included \textsl{SimpleAllocator}
\\\\
\end{tabular}\\
\\
After you are done setting the right options, you can generate a \textbf{controller} by using \textsl{ControllerConfig}'s \textsl{createController} method. All further interactions with your simulation are done through this controller.\\
\\
As a short example, this configuration would give you a Classic DEVS named \texttt{foosim} that saves every 8 cycles:
\begin{verbatim}
ControllerConfig conf = ControllerConfig();
conf.name = "foosim";
conf.saveInterval = 8;

@@

\subsubsection{Loading a previous simulation}
Loading a previous simulation from a savefile follows the same procedure as setting up a regular simulation for the most part.\\
First the simulation is configured (optionally by using the ControllerConfig object as described above) and then, instead of loading a new model, you can use the Controller's \textsl{load} method to load the data of your previous simulation.\\
\\
\textit{Important: to load a simulation you \textbf{do not} have to use the same configuration!}
\\
If you wish to increase the amount of cores of a loaded simulation, it is recommended to use an allocator which overrides the model's preferred location, since those will still be set to the cores of the previous simulation. The included \textsl{SimpleAllocator} can be used by setting its \texttt{allowUserOverride} flag to \texttt{false} in the constructor. Reducing the amount of cores is handled automatically.

### 2015-05-26 manual/tex/example.tex
Updated manual (Controller), added example simulations

Extensive examples are provided in our Controller testing classes. For each formalism a model was created which the user can use as a reference implementation.\\

\subsection{example}

\begin{lstlisting}
std::ofstream filestream("controller/devstestcoupled.txt");
{
	CoutRedirect myRedirect(filestream);
	auto tracers = createObject<n_tracers::t_tracerset>();

	std::unordered_map<std::size_t, t_coreptr> coreMap;
	std::shared_ptr<Allocator> allocator = 
		createObject<SimpleAllocator>(1);
	std::shared_ptr<n_control::LocationTable> locTab = 
		createObject<n_control::LocationTable>(1);

	t_coreptr c = createObject<Core>();
	coreMap[0] = c;

	Controller ctrl("testController", coreMap, allocator, 
		locTab, tracers);
	ctrl.setClassicDEVS();
	ctrl.setTerminationTime(t_timestamp(360, 0));

	t_coupledmodelptr m1 = createObject<n_examples_coupled::
		TrafficSystem>("trafficSystem");
	ctrl.addModel(m1);

	ctrl.simulate();
	EXPECT_TRUE(c->isLive() == false);
	EXPECT_TRUE(c->getTime() >= t_timestamp(360, 0));
};
\end{lstlisting}

>>>>

The following are a few quick examples to illustrate the setup of a regular simulation.\\
Additionally, many working examples are provided in our Controller testing classes (\texttt{controllertest.cpp}). For each formalism a model was created which the user can use as a reference implementation.\\

\section{Classic DEVS}
The following example describes the manual setup of a crowd simulation in a zoo:
\begin{Verbatim}[fontsize=\small]
// Setting up all prerequisites
auto tracers = createObject<n_tracers::t_tracerset>();
std::unordered_map<std::size_t, t_coreptr> coreMap;
std::shared_ptr<Allocator> allocator = createObject<SimpleAllocator>(1);
std::shared_ptr<n_control::LocationTable> locTab = createObject<n_control::LocationTable>(1);

// Setting up the core
t_coreptr c = createObject<Core>();
coreMap[0] = c;

// Setup of the controller
Controller ctrl("zooSim", coreMap, allocator, locTab, tracers);
ctrl.setClassicDEVS();
ctrl.setTerminationTime(t_timestamp(360, 0));

// Creating and adding the main model
t_coupledmodelptr m1 = createObject<n_crowdSim::Zoo>("Planckendael");
ctrl.addModel(m1);

// Starting the simulation
ctrl.simulate();
\end{Verbatim}

In cases where you don't need control over all individual components, it's even quicker to opt for using \textsl{ControllerConfig} to set up everything:

\begin{Verbatim}[fontsize=\small]
// Creating a ControllerConfig object, setting all non-default parameters
ControllerConfig conf;
conf.name = "zooSim";

auto ctrl = conf.createController();
ctrl->setTerminationTime(t_timestamp(360, 0));

t_coupledmodelptr m1 = createObject<n_crowdSim::Zoo>("Planckendael");
ctrl->addModel(m1);

ctrl->simulate();
\end{Verbatim}

\section{Parallel DEVS (Optimistic)}
The simulation of the air traffic on an airport:
\begin{Verbatim}[fontsize=\small]
\\ Setup of the prerequisites
auto tracers = createObject<n_tracers::t_tracerset>();
t_networkptr network = createObject<Network>(2);
std::unordered_map<std::size_t, t_coreptr> coreMap;
std::shared_ptr<Allocator> allocator = createObject<SimpleAllocator>(2);
std::shared_ptr<n_control::LocationTable> locTab = createObject<n_control::LocationTable>(2);

\\ Setup of the cores
t_coreptr c1 = createObject<Multicore>(network, 0, locTab, 2);
t_coreptr c2 = createObject<Multicore>(network, 1, locTab, 2);
coreMap[0] = c1;
coreMap[1] = c2;

\\ Setup of the controller
Controller ctrl("AirControl", coreMap, allocator, locTab, tracers);
ctrl.setPDEVS();
ctrl.setTerminationTime(t_timestamp(720, 0));

\\ Creating and adding the main model
t_coupledmodelptr m = createObject<n_airControl::Airport>("JFK");
ctrl.addModel(m);

ctrl.simulate();
\end{Verbatim}

Here too, the setup is shorter and easier using \textsl{ControllerConfig}:

\begin{Verbatim}[fontsize=\small]
ControllerConfig conf;
conf.name = "AirControl";
conf.simType = Controller::PDEVS;
conf.coreAmount = 2;

auto ctrl = conf.createController();
ctrl->setTerminationTime(t_timestamp(720, 0));

t_coupledmodelptr m1 = createObject<n_airControl::Airport>("JFK");
ctrl->addModel(m1);
ctrl->simulate();
\end{Verbatim}
